---
title: "Linear regression"
output:
  html_document:
    theme: cerulean
    toc: yes
    toc_depth: 3
    number_sections: false
    toc_float: 
       collapsed: true
    #code_folding: hide
---

```{=html}
<style>
h2 {
  background-color: #D4DAEC;
}
body{
  font-size: 14pt;
}
</style>
```

## Introduction


-   Motivation
-   Data assumptions
-   Perform the linear regression analysis
-   Model evaluation



## Prepare data

**fev** data: Smoking tends to impair lung function. Data in children who smoke.

**age**: subject age
**smoke**: smoke smoking habits (1 = yes, 2 = no)

```{r}

#dataForAnalysis=read.csv("./data/fev.csv",header=TRUE,row.names=1)
dataForAnalysis <- read.csv("https://raw.githubusercontent.com/couthcommander/sip_computing/main/labs/fev.csv",header=TRUE,row.names=1)
dataForAnalysis$sex=ifelse(dataForAnalysis$sex==1,"male","female")
dataForAnalysis$smoke=ifelse(dataForAnalysis$smoke==1,"yes","no")

head(dataForAnalysis)

```

## Simple linear regression

**Question**: Does age associated with fev (lung function )?

### Data assumptions

**Normality**: dependent variable follows a normal distribution


```{r}

hist(dataForAnalysis$age)
hist(dataForAnalysis$fev)

```

**Linearity**: The relationship between the independent and dependent variable must be linear.

```{r}

plot(fev ~ age, data = dataForAnalysis)

```

### Perform the linear regression analysis

fev=b0+b1*Age

```{r}

modelResult <- lm(fev ~ age, data = dataForAnalysis)

summary(modelResult)


```

Model Interpretation:

the *Coefficients* estimates of the beta coefficients, Intercept (b0)=0.431648 and age (b1)=0.222041

the standard errors (SE), which defines the accuracy of beta coefficients. For a given beta coefficient, the SE reflects how the coefficient varies under repeated sampling. 

the t-statistic and the associated p-value, which defines the statistical significance of the beta coefficients.


the estimated regression equation can be written as follow: fev = 0.431648 + 0.222041*age

the intercept (b0) It can be interpreted as the predicted fev value at age zero.

the beta coefficient (slope) for age (b1) is 0.222041. It means with age increase in one year, the predicted fev value will increase 0.222041.


The R-squared (R2) ranges from 0 to 1 and represents the proportion of information in the data that can be explained by the model. For a simple linear regression, R2 is the square of the Pearson correlation coefficient.

The adjusted R-squared adjusts for the degrees of freedom.



### Model evaluation

#### Confidence interval of Coefficients

```{r}

confint(modelResult)

```

The standard error measures the variability/accuracy of the beta coefficients. It can be used to compute the confidence intervals of the coefficients. There is approximately a 95% chance that the interval [0.2072777, 0.2368043] will contain the true value of b1.

#### Visulization of the fitted line

```{r}

plot(dataForAnalysis$age,dataForAnalysis$fev,main = "FEV Regression by Age")
abline(modelResult,cex = 1.3,pch = 16,xlab = "FEV",ylab = "Age")

```


#### Residuals distribution

```{r}

plot(modelResult$fitted.values,modelResult$residuals,xlab="Fitted Values",ylab="Residuals")

qqnorm(scale(modelResult$residuals))
abline(0,1,lty=2,col="red")

```


### Predict new data

```{r}

newData <- data.frame(age = c(Subject1=3,Subject2=4))
predict(modelResult,newData)


```



## Multiple linear regression


Multiple linear regression is an extension of simple linear regression used to predict an outcome based on multiple predictors.

**Question**: Are age and smoking associated with fev (lung function)?


### Data visulization


```{r}

boxplot(dataForAnalysis$fev~dataForAnalysis$smoke)

boxplot(dataForAnalysis$age~dataForAnalysis$smoke)

```



### Perform the linear regression analysis

```{r}

modelResult <- lm(fev ~ age+smoke, data = dataForAnalysis)

summary(modelResult)
confint(modelResult)

```


Model Interpretation:

the estimated regression line equation can be written as follow: fev = 0.367373 + 0.230605* age-0.208995*Smoke(Yes)

the beta coefficient for the variable age (b1) is 0.230605. It means with age increase in one year, the predicted fev value will increase 0.230605

the beta coefficient for the variable smoke (b2) is -0.208995. It means the predicted fev value will be smaller (-0.208995) in smokers.

F-statistic gives the overall significance of the model. It assess whether at least one predictor variable has a non-zero coefficient.


### Effects of variables

```{r}

library(effects)
plot(allEffects(modelResult))


```





