---
title: "Linear regression"
output:
  html_document:
    theme: cerulean
    toc: yes
    toc_depth: 3
    number_sections: false
    toc_float: 
       collapsed: true
    #code_folding: hide
---

```{=html}
<style>
h2 {
  background-color: #D4DAEC;
}
</style>
```

```{r setup,echo=FALSE}

knitr::opts_chunk$set(echo = FALSE,eval=FALSE)


```



## Exercise

-   Data assumptions: show data distribution and discuss about Normality and Linearity
-   Perform the linear regression analysis
-   Model evaluation: discuss model result


## Data

```{r,echo=TRUE}

#load data
dataForAnalysis <- read.csv("https://raw.githubusercontent.com/couthcommander/sip_computing/main/labs/sot-covid.csv",header=TRUE,row.names=1)

dataForAnalysis$organ=factor(dataForAnalysis$organ)

head(dataForAnalysis)

```

**Question**: Is ECD at three weeks (ecd2) associated with basedline ECD (ecd1) and other factors including organ and age?

### Exercise 1: Data visulization for ecd2, ecd1, age, and organ

```{r}

plot(dataForAnalysis[,c("ecd2","ecd1","age")])

boxplot(dataForAnalysis$ecd2~dataForAnalysis$organ)

```


### Exercise 2: Perform the linear regression analysis, ecd2~ecd1+age+organ

```{r}

modelResult <- lm(ecd2~ecd1+age+organ, data = dataForAnalysis)

```


### Exercise 3: Model interpretation, show coefficients, confidence interval, and p values 

```{r}

summary(modelResult)
confint(modelResult)

```






