---
title: "Logistic Regression"
output:
  html_document:
    theme: cerulean
    toc: yes
    toc_depth: 3
    number_sections: false
    toc_float: 
       collapsed: true
    #code_folding: hide
---

```{=html}
<style>
h2 {
  background-color: #D4DAEC;
}
body{
  font-size: 14pt;
}
</style>
```



```{r setup,echo=FALSE}

knitr::opts_chunk$set(echo = TRUE,eval=TRUE)


```



## Exercise

-   Data overview
-   Perform logistic regression analysis
-   Model evaluation


```{r,message=FALSE,echo=TRUE,eval=TRUE}

#Get Titanic data
library(Hmisc)
getHdata(titanic3)
head(titanic3)


```

**Question**: Is survival (survived=1) associated with age, sex and ticket class (pclass)?

### Exercise 1: Data visualization for survival, age, sex and pclass


```{r}

table(titanic3$survived,titanic3$sex)

table(titanic3$survived,titanic3$pclass)

tapply(titanic3$age,titanic3$survived,summary)
boxplot(titanic3$age~titanic3$survived)


```


### Exercise 2: Perform logistic regression analysis

survived ~ age+pclass+sex

```{r}

modelResult <- glm(survived ~ age+pclass+sex, data = titanic3,family = "binomial")
summary(modelResult)


```

### Exercise 3: Model interpretation, show coefficients, confidence interval, and p values 

```{r}

confint(modelResult)

```


### Exercise 4: Report odds ratio for each variable


```{r}

#Odds ratio
exp(modelResult$coefficients)


```

### Exercise 5: Show effect of each variable

```{r,message=FALSE}

library(effects)
#allEffects(modelResult)
plot(allEffects(modelResult))


```







