---
title: "Logistic Regression"
output:
  html_document:
    theme: cerulean
    toc: yes
    toc_depth: 3
    number_sections: false
    toc_float: 
       collapsed: true
    #code_folding: hide
---

```{=html}
<style>
h2 {
  background-color: #D4DAEC;
}
body{
  font-size: 14pt;
}
</style>
```
## Introduction

-   Motivation
-   Data overview
-   Perform logistic regression analysis
-   Model evaluation

## Prepare data

**fev** data: Smoking tends to impair lung function. Data in children who smoke.

**age**: subject age

**smoke**: smoke smoking habits (1 = yes, 2 = no)

```{r}

#fev=read.csv("./data/fev.csv",header=TRUE,row.names=1)
fev <- read.csv("https://raw.githubusercontent.com/couthcommander/sip_computing/main/labs/fev.csv",header=TRUE,row.names=1)
fev$sex=ifelse(fev$sex==1,"male","female")
fev$smoke=factor(ifelse(fev$smoke==1,"yes","no"))

head(fev)

```

## Simple Logistic regression

**Question**: Does smoking associated with age?

### Logistic regression assumptions

-   The outcome is a binary or dichotomous variable like yes vs no, positive vs negative, 1 vs 0.
-   The Observations are Independent.
-   There is a linear relationship between the logit of the outcome and each predictor variables. logit(p) = log($\frac{p}{1-p}$), where p is the probabilities of being the outcome (for example, being yes).
-   There is no extreme values or outliers in the continuous predictors
-   There is no high multicollinearity among the predictors.

### Data visulization

```{r}

table(fev$smoke)
hist(fev$age)

boxplot(fev$age~fev$smoke)

```

### Perform logistic regression analysis

logit(p Smoking)=log($\frac{p}{1-p}$)=b0+b1\*Age

```{r}

modelResult <- glm(smoke ~ age, data = fev,family = "binomial")
summary(modelResult)


```

Model Interpretation:

the *Coefficients* estimates of the beta coefficients, Intercept (b0)=-7.74391 and age (b1)=0.48364

the standard errors (SE), which defines the accuracy of beta coefficients. For a given beta coefficient, the SE reflects how the coefficient varies under repeated sampling.

the z value and the associated p-value, which defines the statistical significance of the beta coefficients.

the estimated regression equation can be written as follow: log($\frac{p}{1-p}$) = -7.74391 + 0.48364\*age

Alternatively, the equation can be written as: $\frac{e^{(-7.74391 + 0.48364* age)}}{1+e^{(-7.74391 + 0.48364* age)}}$

As a result, we can predict the probability (p) of being a smoker for a specific age value.

### Predict new data

```{r}

newData <- data.frame(age = c(Subject1=6,Subject2=16))
predictionResult=predict.glm(modelResult,newData,type ="response") #probabilities
predictionResult

```

### Odds ratio

logit(p Smoking)=log($\frac{p}{(1-p)}$) is also called as log-odds.

The $\frac{p}{(1-p)}$ is called odds, or odds of success. It reflect the likelihood that the event will occur. It can be seen as the ratio of "successes" to "non-successes".

Odds ratio is the ratio between two odds:

$$\frac{(p1/(1-p1))}{(p2/(1-p2))}$$
It represents the ratio of the odds that an event will occur (for example, being a smoker) in one situation (for example, age = 2), compared to the odds of the event occurring (being a smoker) in the another situation (for example, age = 1). In this example, Odds ratio measures the association between a predictor variable (age) and the outcome variable (being smoker).

Based on the equation from model, log($\frac{p}{1-p}$) = -7.74391 + 0.48364\*age. We can get the Odds Ratio between Age1 vs Age2:
$e^{(-7.74391 + 0.48364*Age1)}/e^{(-7.74391 + 0.48364*Age2)}$

=$e^{(-7.74391 + 0.48364*Age1)-(7.74391 + 0.48364*Age2)}$

=$e^{0.48364*(Age1-Age2)}$

It indicates with one year age increase, the odds of being a smoker will increase $e^{0.48364*1}=1.62$

So we will report the odds ratio of Age by taking an exponential transformation of its coefficient. $e^{0.48364}=1.62$


```{r}

#odds ratio
exp(coefficients(modelResult))

#CI for odds ratio
exp(confint(modelResult))

```

## Multiple logistic regression

**Question**: Does smoking associated with age, height, and sex?

### Data visulization

```{r}

table(fev$sex,fev$smoke)
plot(fev[,c("age","height")])

boxplot(fev$height~fev$smoke)


```

### Perform logistic regression analysis

```{r}

modelResult <- glm(smoke ~ age+height+sex, data = fev,family = "binomial")
summary(modelResult)

```

### Effects of variables

```{r,message=FALSE}

library(effects)
plot(allEffects(modelResult),axes=list(x=list(rug=FALSE)))


```
