---
title: "Logistic Regression Exercises"
output:
  html_document:
    theme: cerulean
    toc: yes
    toc_depth: 3
    number_sections: false
    toc_float: 
       collapsed: true
    #code_folding: hide
---

```{=html}
<style>
h2 {
  background-color: #D4DAEC;
}
body{
  font-size: 14pt;
}
</style>
```



```{r setup,echo=FALSE}

knitr::opts_chunk$set(echo = FALSE, eval=FALSE)


```



## Exercise

-   Exploratory data analysis
-   Perform logistic regression analysis
-   Interpretation  of the results

### Example data

```{r,message=FALSE, echo=TRUE, eval=TRUE}

#Get Titanic data
library(Hmisc)
getHdata(titanic3)
head(titanic3)
label(titanic3$survived) <- 'survived (1 = Yes, 2 = No)'
# titanic3$survived=ifelse(titanic3$survived==1,"Yes", "No")

```

**Question**: Is the probability of being survival associated with age, sex and, ticket class (`pclass`)?

### Exercise 1: Exploratory data analysis - understanding the data

```{r}

(tt1 <- table(titanic3$survived, titanic3$sex))
rowsum1 <- apply(tt1, 1, sum)
tt1[1,]/rowsum1[1]
tt1[2,]/rowsum1[2]

(tt2 <- table(titanic3$survived, titanic3$pclass))
rowsum2 <- apply(tt2, 1, sum)
tt2[1,]/rowsum2[1]
tt2[2,]/rowsum2[2]

tapply(titanic3$age, titanic3$survived, summary)

boxplot(titanic3$age ~ titanic3$survived, main="", ylab="Age", xlab="Survived")

```


### Exercise 2: Perform logistic regression analysis and interpretation of results 

survived ~ age + pclass + sex

```{r}

modelResult <- glm(survived ~ age + pclass + sex, data = titanic3, family = "binomial")
summary(modelResult)

confint(modelResult)

#Odds ratio
exp(modelResult$coefficients)

```

### Exercise 3: Effects of each variable

```{r,message=FALSE}

library(effects)
plot(allEffects(modelResult))


```







