---
title: "Simple linear regression"
output:
  html_document:
    theme: cerulean
    toc: yes
    toc_depth: 3
    number_sections: false
    toc_float: 
       collapsed: true
    #code_folding: hide
---

```{=html}
<style>
h2 {
  background-color: #D4DAEC;
}
</style>
```

## Introduction of the methods (recapture the course)


-   Motivation
-   Data assumptions
-   Perform the linear regression analysis
-   Model evaluation


## Lecture

Short introduction about data and Motivations here.

```{r}

dataForAnalysis=mtcars

```

### Data assumptions


**Normality**: dependent variable follows a normal distribution


```{r}

hist(dataForAnalysis$mpg)

```


**Linearity**: The relationship between the independent and dependent variable must be linear.

```{r}

plot(mpg ~ hp, data = dataForAnalysis)

```

### Perform the linear regression analysis

```{r}

modelResult <- lm(mpg ~ hp, data = dataForAnalysis)

summary(modelResult)

```

### Model evaluation


```{r}
plot(dataForAnalysis$hp,dataForAnalysis$mpg,main = "MPG Regression by Horse Power",
abline(modelResult),cex = 1.3,pch = 16,xlab = "Horsepower",ylab = "MPG")


```


```{r}

op=par(mfrow=c(2,2),mar=c(4,4,2,2))
plot(modelResult)

par(op)

```



### Predict new data

```{r}

newData <- data.frame(hp = c(NewCar1=110,NewCar2=170))
result <-  predict(modelResult,newData)
print(result)


```





